\documentclass[12pt]{ucsddissertation}
% mathptmx is a Times Roman look-alike (don't use the times package)
% It isn't clear if Times is required. The OGS manual lists several
% "standard fonts" but never says they need to be used.
\usepackage{mathptmx}
\usepackage{natbib}
\usepackage[NoDate]{currvita}
\usepackage{array}
\usepackage{tabularx}
\usepackage{booktabs}
\usepackage{ragged2e}
\usepackage{microtype}
\usepackage{xcolor}
\usepackage[breaklinks=true,pdfborder={0 0 0}]{hyperref}
\usepackage{graphicx}
\usepackage{amsmath, amsfonts, amssymb}
\usepackage{dsfont}
\usepackage{nicefrac}
\usepackage{mathtools}
\usepackage[ruled, lined, linesnumbered, commentsnumbered, longend]{algorithm2e}
\usepackage{amsthm}
\usepackage{wrapfig}
\usepackage{geometry} 
\usepackage{subcaption}
\captionsetup[sub]{font=scriptsize,labelfont={bf}}
\usepackage[breakable, theorems, skins]{tcolorbox}
\usepackage[capitalize,noabbrev]{cleveref}
\AtBeginDocument{%
	\settowidth\cvlabelwidth{\cvlabelfont 0000--0000}%
}

% OGS recommends increasing the margins slightly.
\increasemargins{.1in}

% These are just for testing/examples, delete them
\usepackage{trace}
%\usepackage{showframe} % This package was just to see page margins
\usepackage[english]{babel}
\usepackage{blindtext}
\overfullrule5pt
% ---

%%For multi-file compilation 
%\usepackage{subfiles}

% Required information
\title{The Primacy of Applied Privacy}
\author{Casey Meehan}
\degree{Computer Science}{Doctor of Philosophy}
% Each member of the committee should be listed as Professor Foo Bar.
% If Professor is not the correct title for one, then titles should be
% omitted entirely.
\chair{Professor Kamalika Chaudhuri}
% Your committee members (other than the chairs) must be in alphabetical order
\committee{Professor Taylor Berg-Kirkpatrick}
\committee{Professor Sanjoy Dasgupta}
\committee{Professor Alon Orlitsky}
\degreeyear{2023}

% Start the document
\begin{document}
% Begin with frontmatter and so forth
\frontmatter
\maketitle
\makecopyright
\makesignature
% Optional
\begin{dedication}
\setsinglespacing
\raggedright % It would be better to use \RaggedRight from ragged2e
\parindent0pt\parskip\baselineskip
Something nice
\end{dedication}
% Optional
\begin{epigraph}
\vskip0pt plus.5fil
\setsinglespacing
%{\flushright
%True ease in writing comes from art, not chance,\\
%As those move easiest who have learn'd to dance.\\
%'T is not enough to no harshness gives offence,---\\
%The sound must seem an echo to the sense.
%
%\vskip\baselineskip
%\textit{Alexander Pope}\par}
\vfil
\begin{center}
Something pithy

\vskip\baselineskip
\textit{Someone smart}
\end{center}
\vfil
%\noindent Writing, at its best, is a lonely life. Organizations for
%writers palliate the writer's loneliness, but I doubt if they improve
%his writing. He grows in public stature as he sheds his loneliness and
%often his work deteriorates. For he does his work alone and if he is a
%good enough writer he must face eternity, or the lack of it, each day.
%
%\vskip\baselineskip
%\hskip0pt plus1fil\textit{Ernest Hemingway}\hskip0pt plus4fil\null

%\vfil
\end{epigraph}

% Next comes the table of contents, list of figures, list of tables,
% etc. If you have code listings, you can use \listoflistings (or
% \lstlistoflistings) to have it be produced here as well. Same with
% \listofalgorithms.
\tableofcontents
\listoffigures
\listoftables

% Preface
\begin{preface}
Almost nothing is said in the manual about the preface. There is no
indication about how it is to be typeset. Given that, one is forced to
simply typeset it and hope it is accepted. It is, however, optional
and may be omitted.
\end{preface}

% Your fancy acks here. Keep in mind you need to ack each paper you
% use. See the examples here. In addition, each chapter ack needs to
% be repeated at the end of the relevant chapter.
\begin{acknowledgements}
I would like to acknowledge Professor Eta Theta for his support as the
chair of my committee. Through multiple drafts and many long nights,
his guidance has proved to be invaluable.

I would also like to acknowledge the ``Smith Clan'' of lab~28, without
whom my research would have no doubt taken fives times as long. It is
their support that helped me in an immeasureable way.

Chapter 2, in full, is a reprint of the material as it appears in
Numerical Grid Generational in Computational Fluid Mechanics~2009.
Smith, Laura; Smith, Jane~D., Pineridge Press,~2009. The dissertation
author was the primary investigator and author of this paper.

Chapter 3, in part, has been submitted for publication of the material
as it may appear in Education Mechanics,~2009, Smith, Laura; Smith,
Jane~D., Trailor Press,~2009. The dissertation author was the primary
investigator and author of this paper.

Chapter 5, in part is currently being prepared for submission for
publication of the material. Smith, Laura; Smith, Jane~D\@. The
dissertation author was the primary investigator and author of this
material.
\end{acknowledgements}

% Stupid vita goes next
\begin{vita}
\noindent
\begin{cv}{}
\begin{cvlist}{}
\item[1996] Bachelor of Arts, University of California, Berkeley
\item[1996--2000] U.S. Marines
\item[2000--2002] Teaching Assistant, Department of Mechanical
Engineering\\University of California, San Diego
\item[2002--2006] Research Assistant, University of California, San
Diego
\item[2010] Doctor of Philosophy, University of California, San Diego
\end{cvlist}
\end{cv}

% This puts in the PUBLICATIONS header. Note that it appears inside
% the vita environment. It is optional.
\publications
\noindent``Distributions of Control Points in a System for Analysis of Stress
Distribution'' IRE Transactions of the I.R.E\@. Professional Group on
Automatic Control, vol. AC-7, pp 272--289, September 2005

% This puts in the FIELDS OF STUDY. Also inside vita and also
% optional.
\fieldsofstudy
\noindent Major Field: Engineering (Specialization or Focused Studies)
\vskip\baselineskip
Studies in Applied Mathematics\par
Professors Alpha Beta and Gamma Delta
\vskip\baselineskip
Studies in Mechanices\par
Professors Epsilon Zeta and Eta Theta
\vskip\baselineskip
Studies in Electromagnetism\par
Professors Iota Kappa and Lambda Mu
\end{vita}

% Put your maximum 350 word abstract here.
\begin{dissertationabstract}
The Abstract begins here. The abstract is limited to 350 words for a
doctoral dissertation. It should consist of a short statement of the
problem, a brief explanation of the methods and procedures employed in
generating the data, and a condensed summary of the findings of the
study. The abstract may continute onto a second page if necessary. The
text of the abstract must be double spaced.
\end{dissertationabstract}

% This is where the main body of your dissertation goes!
\mainmatter

% Optional Introduction
\begin{dissertationintroduction}
This optional section is barely described in the OGS manual other than
saying it is optional and that it appears in the table of contents
between the Abstract and the first chapter.

No formatting guidelines appear so presumably, it should be formatted
like an ordinary chapter. It should appear after the
\verb!\mainmatter! macro because it should start on page~1.
\end{dissertationintroduction}

%\chapter{An ordinary page}
%The purpose of this page is to illustrate an ordinary page of text in
%a doctoral dissertation or master's thesis. All pages of the doctoral
%dissertation or master's thesis must be kept within the margins of
%1.5'' on the left, 1'' on the right, 1'' on the top and 1.25'' on the
%bottom. All text must be double spaced except as indicated below.
%
%It is recommended that to increase the margins as paper can shift in a
%printer and as some photocopiers tend to increase the image being
%copied.
%
%The first line of each paragraph must be indented at least one 0.5''
%tab, as done here.
%
%This text is intended to be a part of the dissertation, for a doctoral
%student, or the thesis if you are receiving a master's degree, and now
%a quote is included here:
%\begin{quote}
%All quotes of more than six lines, even though this one is not, are to
%be indented 0.5'' from the left and 0.5'' from the right. These longer
%quotes are to be single spaced. Don't forget to adjust for proper
%spacing after the last line of the quoted material.
%\end{quote}
%The rest of the paragraph would continue as so.

\include{chapters/chapter1/chapter1}
\include{chapters/chapter2/chapter2}
\include{chapters/chapter3/chapter3}

\appendix
%\Blinddocument
\include{chapters/chapter1/appendix1}
\include{chapters/chapter2/appendix2}
\include{chapters/chapter3/appendix3}

% Stuff at the end of the dissertation goes in the back matter
\backmatter
\bibliographystyle{plain} % Or whatever style you want like plainnat
\bibliography{references}

\end{document}
