\documentclass[12pt]{ucsddissertation}
% mathptmx is a Times Roman look-alike (don't use the times package)
% It isn't clear if Times is required. The OGS manual lists several
% "standard fonts" but never says they need to be used.
\usepackage{mathptmx}
\usepackage[numbers]{natbib}
\usepackage[NoDate]{currvita}
\usepackage{array}
\usepackage{tabularx}
\usepackage{booktabs}
\usepackage{ragged2e}
\usepackage{microtype}
\usepackage{xcolor}
\usepackage[breaklinks=true,pdfborder={0 0 0}]{hyperref}
\usepackage{graphicx}
\usepackage{amsmath, amsfonts, amssymb}
\usepackage{dsfont}
\usepackage{nicefrac}
\usepackage{mathtools}
\usepackage[ruled, lined, linesnumbered, commentsnumbered, longend]{algorithm2e}
\usepackage{amsthm}
\usepackage{wrapfig}
\usepackage{geometry}
\usepackage{soul}
\usepackage{lipsum}
\usepackage{tikz}
\usetikzlibrary{bayesnet}
\usepackage{bbm}
\usepackage{subcaption}
\usepackage{yfonts}
\captionsetup[sub]{font=scriptsize,labelfont={bf}}
\usepackage[breakable, theorems, skins]{tcolorbox}
\usepackage[capitalize,noabbrev]{cleveref}
\AtBeginDocument{%
	\settowidth\cvlabelwidth{\cvlabelfont 0000--0000}%
}

\DeclareMathOperator*{\argmax}{arg\,max}
\DeclareMathOperator*{\argmin}{arg\,min}

% OGS recommends increasing the margins slightly.
\increasemargins{.1in}

% These are just for testing/examples, delete them
\usepackage{trace}
%\usepackage{showframe} % This package was just to see page margins
\usepackage[english]{babel}
\usepackage{blindtext}
\overfullrule5pt
% ---

%%For multi-file compilation 
%\usepackage{subfiles}

% Required information
\title{Theoretical Foundations of Trustworthy Machine Learning}
\author{Robi Bhattacharjee}
\degree{Computer Science}{Doctor of Philosophy}
% Each member of the committee should be listed as Professor Foo Bar.
% If Professor is not the correct title for one, then titles should be
% omitted entirely.
\chair{Professor Kamalika Chaudhuri}
% Your committee members (other than the chairs) must be in alphabetical order
\committee{Professor Mikhail Belkin}
\committee{Professor Sanjoy Dasgupta}
\committee{Professor Yoav Freund}

\degreeyear{2023}


% Start the document
\begin{document}
% Begin with frontmatter and so forth
\frontmatter
\maketitle
\makecopyright
\makesignature
% Optional
\begin{dedication}
\setsinglespacing
\raggedright % It would be better to use \RaggedRight from ragged2e
\parindent0pt\parskip\baselineskip
For Mom, Dad, and Sormeh.  
\end{dedication}

%% Optional
%\begin{epigraph}
%\vskip0pt plus.5fil
%\setsinglespacing
%%{\flushright
%%True ease in writing comes from art, not chance,\\
%%As those move easiest who have learn'd to dance.\\
%%'T is not enough to no harshness gives offence,---\\
%%The sound must seem an echo to the sense.
%%
%%\vskip\baselineskip
%%\textit{Alexander Pope}\par}
%\vfil
%\begin{center}
%Something pithy
%
%\vskip\baselineskip
%\textit{Someone smart}
%\end{center}
%\vfil
%%\noindent Writing, at its best, is a lonely life. Organizations for
%%writers palliate the writer's loneliness, but I doubt if they improve
%%his writing. He grows in public stature as he sheds his loneliness and
%%often his work deteriorates. For he does his work alone and if he is a
%%good enough writer he must face eternity, or the lack of it, each day.
%%
%%\vskip\baselineskip
%%\hskip0pt plus1fil\textit{Ernest Hemingway}\hskip0pt plus4fil\null
%
%%\vfil
%\end{epigraph}

% Next comes the table of contents, list of figures, list of tables,
% etc. If you have code listings, you can use \listoflistings (or
% \lstlistoflistings) to have it be produced here as well. Same with
% \listofalgorithms.
\tableofcontents
\listoffigures
\listoftables

%% Preface
%\begin{preface}
%Almost nothing is said in the manual about the preface. There is no
%indication about how it is to be typeset. Given that, one is forced to
%simply typeset it and hope it is accepted. It is, however, optional
%and may be omitted.
%\end{preface}

% Your fancy acks here. Keep in mind you need to ack each paper you
% use. See the examples here. In addition, each chapter ack needs to
% be repeated at the end of the relevant chapter.
\begin{acknowledgements}
First and foremost, I thank my advisor, Kamalika, for her guidance over my time in graduate school. Much of what I understand about conducting and communicating machine learning research, I owe directly to her mentorship. Beyond research, Kamalika has always been genuine and forthcoming to me with advice and guidance for shaping my academic career. 

I also thank my co-advisor, Sanjoy. His emphasis on simplicity and elegance has been a huge inspiration for my style of research. Additionally his willingness to listen to and give feedback for any of my half-baked ideas has been a consistent source of comfort and support. 

None of my research would be possible without all of my amazing collaborators; I'm very grateful to have worked with all of them. I especially want to thank Yoav Freund for  his amazing enthusiastic energy for conducting research, and Michal Moshkovitz for her sharp mathematical insight and careful attention to detail.

My time at UCSD would not have been anywhere near as enjoyable if it weren't for my lab-mates, Casey, Jacob, Yao-Yuan, Amrita, and Mary. I will miss our Wednesday lunches dearly. 

I also want to give special thanks to two people from before my Phd that have deeply shaped my life. My father shared with me his love for mathematics for as long as I can remember. In many ways, this thesis is a direct result of that. Later, through middle school and high school, I prepared for math competitions under Andrew Kahng's guidance. Those years were formative in teaching me how to be a skilled problem solver.

I would not have been able to accomplish anything without the loving support of my friends and family. I especially want to thank my brother Neil, my mother, and my friends Ahmed, Alex, and William. You guys have consistently been people I can rely on in any and all situations.

Finally, to my fiancee Sormeh, none of this would be possible or worth doing without you. 






%
%I cannot overemphasize the gratitude I have to my collaborators as well. First, to my collaborators at FAIR. I thank Chuan Guo for showing me how to navigate incredibly challenging and open-ended ML problems. His Socratic approach to mentoring helped me explore my own instincts and take ownership of the project without letting me slip down the wrong path. Florian Bordes taught me the ins and outs of contemporary vision modeling. Pascal Vincent's insights on how to design deep learning experiments were truly formative; I sincerely appreciate his effort and time. I owe an enormous debt of gratitude to Ashwin Machanavajjhala at Tumult for mentoring me on how how to reason about different privacy definitions and guarantees in applied settings. 
%
%Finally, to all of my friends. To the lab: I could not have landed in a better group. To be surrounded by such wonderful and bright companions is a win --- for them to be your colleagues as well is a gift. To all my dear pre-PhD friends (you know who you are, and you really don't have read this dissertation): you are the loves of my life! 

\pagebreak

\textbf{Chapter 1}, in full, is a reprint of the material as it appears in International Conference on Machine Learning, 2020. Robi Bhattacharjee, Kamalika Chaudhuri. \emph{When are Non-Parametric Methods Robust}. The dissertation author is the primary investigator and author of this paper. 

\textbf{Chapter 2}, in full, is a reprint of the material as it appears in Neural Information Processing Systems, 2021. Robi Bhattacharjee, Kamalika Chaudhuri. \emph{Consistent Non-Parametric Methods for Maximizing Robustness}. The dissertation author is the primary investigator and author of this paper. 

\textbf{Chapter 3}, in full, is a reprint of the material as it appears in International Conference on Machine Learning. 2022. Robi Bhattacharjee,  Somesh Jha, Kamalika Chaudhuri. \emph{Sample Complexity of Robust Linear Classification on Separated Data}. The dissertation author is the primary investigator and author of this paper.

\textbf{Chapter 4}, in full, is a reprint of the material as it appears in International Conference on Algorithmic Learning Theory, 2023. Robi Bhattacharjee, Max Hopkins, Akash Kumar, Hantao Yu, Kamalika Chaudhuri. \emph{Robust Empirical Risk Minimization with Tolerance}. The dissertation author is the primary investigator and author of this paper.

\textbf{Chapter 5}, in full, is a reprint of the material as it appears in International Conference on Machine Learning, 2023. Robi Bhattacharjee, Sanjoy Dasgupta, Kamalika Chaudhuri. \emph{Data-Copying in Generative Models: A Formal Framework}. The dissertation author is the primary investigator and author of this paper. 
\end{acknowledgements}

% Stupid vita goes next
\begin{vita}
\noindent
\begin{cv}{}
\begin{cvlist}{}
\item[2016] Bachelor of Science, Massachusetts Institute of Technology
\item[2022] Master of Science, University of California San Diego
\item[2023] Doctor of Philosophy, University of California San Diego
\end{cvlist}
\end{cv}

%% This puts in the PUBLICATIONS header. Note that it appears inside
%% the vita environment. It is optional.
%\publications
%\noindent``Distributions of Control Points in a System for Analysis of Stress
%Distribution'' IRE Transactions of the I.R.E\@. Professional Group on
%Automatic Control, vol. AC-7, pp 272--289, September 2005

%% This puts in the FIELDS OF STUDY. Also inside vita and also
%% optional.
%\fieldsofstudy
%\noindent Major Field: Engineering (Specialization or Focused Studies)
%\vskip\baselineskip
%Studies in Applied Mathematics\par
%Professors Alpha Beta and Gamma Delta
%\vskip\baselineskip
%Studies in Mechanices\par
%Professors Epsilon Zeta and Eta Theta
%\vskip\baselineskip
%Studies in Electromagnetism\par
%Professors Iota Kappa and Lambda Mu
\end{vita}

% Put your maximum 350 word abstract here.
\begin{dissertationabstract}
%The Abstract begins here. The abstract is limited to 350 words for a
%doctoral dissertation. It should consist of a short statement of the
%problem, a brief explanation of the methods and procedures employed in
%generating the data, and a condensed summary of the findings of the
%study. The abstract may continute onto a second page if necessary. The
%text of the abstract must be double spaced.
Machine learning models have become a ubiquitous part of society, and it has consequently become of paramount importance to understand how to design safe and reliable models. This dissertation attempts to take steps towards this direction by consider two specific problems in reliable machine learning: \textit{adversarial examples,} which are small test-time perturbations to the input designed to cause misclassification, and \textit{data-copying,} which occurs when a generative model simply memorizes its training data (giving poor generalization and dangerous security risks). 
\end{dissertationabstract}

% This is where the main body of your dissertation goes!
\mainmatter

% Optional Introduction
\begin{dissertationintroduction}
\input{intro}  
\end{dissertationintroduction}

%\chapter{An ordinary page}
%The purpose of this page is to illustrate an ordinary page of text in
%a doctoral dissertation or master's thesis. All pages of the doctoral
%dissertation or master's thesis must be kept within the margins of
%1.5'' on the left, 1'' on the right, 1'' on the top and 1.25'' on the
%bottom. All text must be double spaced except as indicated below.
%
%It is recommended that to increase the margins as paper can shift in a
%printer and as some photocopiers tend to increase the image being
%copied.
%
%The first line of each paragraph must be indented at least one 0.5''
%tab, as done here.
%
%This text is intended to be a part of the dissertation, for a doctoral
%student, or the thesis if you are receiving a master's degree, and now
%a quote is included here:
%\begin{quote}
%All quotes of more than six lines, even though this one is not, are to
%be indented 0.5'' from the left and 0.5'' from the right. These longer
%quotes are to be single spaced. Don't forget to adjust for proper
%spacing after the last line of the quoted material.
%\end{quote}
%The rest of the paragraph would continue as so.

\include{chapters/chapter0/chapter1}
\include{chapters/chapter1/chapter1}
\include{chapters/chapter2/chapter2}
\include{chapters/chapter3/chapter3}
\include{chapters/chapter4/chapter4}
%\include{chapters/chapter5/chapter5}
\include{conclusion}


\appendix            
%\Blinddocument
\include{chapters/chapter0/appendix1}
\include{chapters/chapter1/appendix1}
\include{chapters/chapter2/appendix2}
\include{chapters/chapter3/appendix3}
\include{chapters/chapter4/appendix4}
%\include{chapters/chapter5/appendix5}

% Stuff at the end of the dissertation goes in the back matter
\backmatter
\bibliographystyle{unsrtnat} % Or whatever style you want like plainnat
\bibliography{references}

\end{document}
